Forecasting the 2024 US Presidential Election

### 2024-11-03 paper/paper.qmd
update data exploration script add graph in paper

## Overview
The dataset encompasses polling data focused on two candidates, Donald Trump and Kamala Harris. Data has been filtered to include only results from pollsters with a numeric grade above 2.5 to maintain quality and consistency. This selection allows us to focus on higher-rated sources, which may enhance the reliability of predictions. Each record includes information on the pollster, their grading, polling methodology, transparency score, and specific polling results for each candidate.

>>>>

## Overview
The dataset encompasses polling data focused on two candidates, Donald Trump and Kamala Harris. Data has been filtered to include only results from pollsters with a numeric grade above 2.5 to maintain quality and consistency. This selection allows us to focus on higher-rated sources, which may enhance the reliability of predictions. Each record includes information on the pollster, their grading, polling methodology, transparency score, and specific polling results for each candidate.
```{r}
#| label: tbl-raw-data-1
#| tbl-cap: First 6 entries of Raw Dataset with varibles 'state','end_date','sample_size', 'canadidate_name','pct'
#| echo: false
#| warning: false
#| message: false

raw_data <- read_csv(here::here("data/01-raw_data/president_polls.csv"))
#Graph
head_raw_data <- head(raw_data,6)
# Note there is a type in Description within the original data set itself
knitr::kable(head_raw_data[, c(13,15,23,51,52)], format = "simple",col.names = c('State','End date','Sample Size', 'Canadidate Name','PCT'))

```

```{r}
#| label: tbl-analysis-data-1
#| tbl-cap: First 6 entries of Analysis Dataset
#| echo: false
#| warning: false
#| message: false

#Graph
head_analysis_data <- head(president_polls_cleaned_data,6)
# Note there is a type in Description within the original data set itself
knitr::kable(head_analysis_data[, 1:5], format = "simple", col.names = c('State','End date','Sample Size', 'Canadidate Name','PCT'))

```
